%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications and Patents}\vspace*{-0.40cm}
\hfill \descriptionstyle{* equal contribution}\vspace*{-0.30cm}
%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\cvsubsection{Publications}\vspace*{-0.15cm}
\\
%\begin{cvitems}\vspace*{-0.15cm}
\begin{cvenumerate}[1]
\item {Tomasz Palczewski*, \textcolor{gray!99!black}{\textbf{Jaejun Lee*}}, Lenin Mookiah*. Production-Ready Applied Deep Learning. \textbf{\textit{Packt Publishing}}, ISBN: 9781803238050, 1803238054, 2022}
\item \hypertarget{CI-GAN:ICME}{\textcolor{gray!99!black}{\textbf{Jaejun Lee}}, Hyun Chul Lee, Tomasz Palczewski. CI-GAN: Co-Clustering By Information Maximizing Generative Adversarial Networks. \textbf{\textit{ICME}}, 2021}
\item \hypertarget{howl:EMNLP}{Raphael Tang*, \textcolor{gray!99!black}{\textbf{Jaejun Lee*}}, Afsaneh Razi, Julia Cambre, Ian Bicking, Jofish Kaye, Jimmy Lin. Howl: A Deployed, Open-Source Wake Word Detection System. \textbf{\textit{EMNLP-NLPOSS}}, 2020}
\item \hypertarget{show:ACL}{Raphael Tang, \textcolor{gray!99!black}{\textbf{Jaejun Lee}}, Ji Xin, Xinyu Liu, Yaoliang Yu, Jimmy Lin. Showing Your Work Doesn't Always Work. \textbf{\textit{ACL}}, 2020}
\item \hypertarget{DeeBERT:ACL}{Ji Xin, Raphael Tang, \textcolor{gray!99!black}{\textbf{Jaejun Lee}}, Yaoliang Yu, Jimmy Lin. DeeBERT: Dynamic Early Exiting for Accelerating BERT Inference. \textbf{\textit{ACL}}, 2020}
\item \hypertarget{honkling:EMNLP}{\textcolor{gray!99!black}{\textbf{Jaejun Lee}}, Raphael Tang, Jimmy Lin. Honkling: In-Browser Personalization for Ubiquitous Keyword Spotting. \textbf{\textit{EMNLP-IJCNLP}}, 2019}
\item {Ryan Clancy, \textcolor{gray!99!black}{\textbf{Jaejun Lee}}, Zeynep Akkalyoncu Yilmaz, Jimmy Lin. Information Retrieval Meets Scalable Text Analytics: Solr Integration with Spark. \textbf{\textit{SIGIR}}, 2019}
\item \hypertarget{honkling:IUI}{\textcolor{gray!99!black}{\textbf{Jaejun Lee}}, Raphael Tang, Jimmy Lin. Universal Voice-Enabled User Interfaces using JavaScript. \textbf{\textit{IUI}}, 2019}
\end{cvenumerate}
\hfill

\cvsubsection{Patents}
\\
\begin{cvenumerate}[9]\vspace*{-0.15cm}
\item \hypertarget{CI-GAN:International}{\textcolor{gray!99!black}{\textbf{Jaejun Lee}}, Hyun Chul Lee, Tomasz Palczewski. Co-Informatic Generative Adversarial Networks for Efficient Data \\Co-Clustering. \textit{International Patent}, Pub. WO/2021/066530, 2021}
\item \hypertarget{CI-GAN:US}{\textcolor{gray!99!black}{\textbf{Jaejun Lee}}, Hyun Chul Lee, Tomasz Palczewski. Co-Informatic Generative Adversarial Networks for Efficient Data \\Co-Clustering. \textit{US Patent}, Pub. 20210097372, 2021}
\end{cvenumerate}
\hfill

\cvsubsection{Manuscripts}
\\
\begin{cvenumerate}[11]\vspace*{-0.15cm}
\item {\textcolor{gray!99!black}{\textbf{Jaejun Lee}}, Raphael Tang, Jimmy Lin. What Would Elsa Do? Freezing Layers During Transformer Fine-Tuning. \textit{arXiv}: 1911.03090, 2019}
\item {\textcolor{gray!99!black}{\textbf{Jaejun Lee}}, Raphael Tang, Jimmy Lin. JavaScript Convolutional Neural Networks for Keyword Spotting in the Browser: An Experimental Analysis. \textit{arXiv}: 1810.12859, 2018}
\end{cvenumerate}