%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------
\newpage

\cvsection{Professional Development}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\cvsubsection{Teaching Assistantship}
\begin{cventries}
\cventrynodesc
{University of Waterloo, Instructed by Prof. Bill Cowan} % Organization
{CS 452/652 -- Real-time Programming} % Job title
{Waterloo, ON, Canada} % Location
{Fall 2019} % Date(s)
\cventrynodesc
{University of Waterloo, Instructed by Prof. Edith Law} % Organization
{CS 480/680 -- Introduction to Machine Learning} % Job title
{Waterloo, ON, Canada} % Location
{Winter 2019} % Date(s)
\cventry
{University of Waterloo, Instructed by Prof. Jimmy Lin} % Organization
{CS 451/651 -- Data Intensive Distributed Computing} % Job title
{Waterloo, ON, Canada} % Location
{Fall 2018} % Date(s)
{ % Description(s) of tasks/responsibilities\\
\begin{cvitems}
\item {Led weekly discussion sessions consisting of 10$\sim$20 students and held office hours each week to assist those who needed additional support.}
\item {Graded assignments and exams, and conducted exam preparation sessions.}
\end{cvitems}
}
\end{cventries}

\cvsubsection{Academic \& Professional Mentorship}
\begin{cventries}
\cventry
{Research Intern} % Organization
{Allen Tao} % Job title
{Markham, ON, Canada} % Location
{May. 2024 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities\\
\begin{cvitems}
\item {Mentoring a research project on few-shot object and attribute detection.}
\end{cvitems}
}
\cventry
{Research Intern} % Organization
{Sandra Wang} % Job title
{Markham, ON, Canada} % Location
{Mar. 2023 - May. 2024} % Date(s)
{ % Description(s) of tasks/responsibilities\\
\begin{cvitems}
\item {Mentored research projects on 3D scene understanding and few-shot keypoint detection (one paper under review for TAI [\hyperlink{LAM:TAI}{14}]).}
\end{cvitems}
}
\cventry
{Undergraduate Research Assistant} % Organization
{Xinyu (Mavis) Liu} % Job title
{Waterloo, ON, Canada} % Location
{Jan. 2018 - Aug. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities\\
\begin{cvitems}
\item {Mentored a research project on keyword spotting.}
\end{cvitems}
}
\end{cventries}
